Lightning Talk: Software Citation: Process, Principles, and Implementation

### 2016-08-04 meetings/WSSSPE4-lightning-talk/WSSSPE4-lightning-talk.tex
minor edits throughout lightning talk paper

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

@@

\bibitem{bib1}
FORCE11 Software Citation Working Group, ``Software citation use cases,'' \url{https://docs.google.com/document/d/1dS0SqGoBIFwLB5G3HiLLEOSAAgMdo8QPEpjYUaWCvIU}, 2016. Accessed: 2016-07-10.
\bibitem{bib2}
A.~M.~Smith, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group ``Software Citation Principles,'' FORCE2016 Website, \url{https://www.force11.org/software-citation-principles}, 2016. Accessed: 2016-07-10.
\bibitem{bib3}
FORCE11 Software Citation Working Group, GitHub repository, \url{https://github.com/force11/force11-scwg}.  Accessed: 2016-07-10.
\bibitem{bib4}
A.~M.~Smith, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group, ``Software Citation Principles,'', \textit{PeerJ Preprints} 4:e2169v3, 2016. \url{https://doi.org/10.7287/peerj.preprints.2169v3}.

>>>>

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.
\usepackage{hyperref}

@@

\bibitem{bib1}
FORCE11 Software Citation Working Group, ``Software citation use cases,'' \url{https://docs.google.com/document/d/1dS0SqGoBIFwLB5G3HiLLEOSAAgMdo8QPEpjYUaWCvIU}, 2016. Accessed: 2016-07-10.
\bibitem{bib2}
A.~M.~Smith, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group ``Software Citation Principles,'' FORCE2016 Website, \url{https://www.force11.org/software-citation-principles}, 2016. Accessed: 2016-07-10.
\bibitem{bib3}
FORCE11 Software Citation Working Group, GitHub repository, \url{https://github.com/force11/force11-scwg}.  Accessed: 2016-07-10.
\bibitem{bib4}
A.~M.~Smith, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group, ``Software Citation Principles,'' \textit{PeerJ Preprints} 4:e2169v3, 2016. \url{https://doi.org/10.7287/peerj.preprints.2169v3}.
